Reduced plasticity and opportunity for selection in terrestrial ectotherm populations

### 2023-04-03 ms.qmd
writing

In contrast, the opportunity for selection (i.e., the change in physiological variability) did not depend on a populations thermal variability or predictability (@fig-5).

>>>>

In contrast, the opportunity for selection (i.e., the change in physiological variability) did not depend on a populations thermal variability or predictability across any of the habitats (@fig-5).
